Hypertension statistics for US adults: an open-source web application for analysis and visualization of US NHANES data

### 2022-10-23 paper/manuscript.Rmd
PM edits, fpath fix attempt

@@

With an open-source software license and publicly available documentation and data, the web application we developed can be extended. The current manuscript described a set of hypertension variables and a sub-population of NHANES participants with data on BP and antihypertensive medication use. The application’s interface and its supporting R package allows additional variables to be added. In addition, the application may be extended to include data from additional NHANES cycles as they become available.

@@

This study has a number of strengths. We used NHANES data, which are publicly available, rigorously collected, and allow for estimation of nationally representative statistics. Also, we leveraged open-source software to ensure that our application is transparent, able to be extended, and freely available. This study also has several limitations. First, NHANES participants had their mean BP measured during a single visit, and BP guidelines recommend obtaining mean BP using at least two BP values measured on separate days. Second, the response rate for NHANES has declined from 1999-2000 through 2017-2020. Effects of this decline are unclear.

>>>>

<br>

@@

<br>

With an open-source software license and publicly available documentation and data, the web application we developed can be extended. The current manuscript described a set of hypertension variables and a sub-population of NHANES participants with data on BP and antihypertensive medication use. The application’s interface and its supporting R package allows additional variables to be added. In addition, the application can be extended to include data from additional NHANES cycles as they become available.

<br>

@@

This study has a number of strengths. We used NHANES data, which are publicly available, rigorously collected, and allow for estimation of nationally representative statistics. Also, we leveraged open-source software to ensure that our application is transparent, able to be extended, and freely available. This study also has several limitations. NHANES participants had their mean BP measured during a single visit, and BP guidelines recommend obtaining mean BP using at least two BP values measured on separate days. The response rate for NHANES has declined from 1999-2000 through 2017-2020. Effects of this decline are unclear.

<br>
